\documentclass[12pt,a4paper]{article}


\input{../header.tex}

\begin{document}

\exerciseSet{10}{January 24, 2023}

\setcounter{AUFGABE}{32}



\aaa{Existence result for constrained minimization.} Prove the following theorem from the lecture:

Let $X$ denote a reflexive Banach space, and let $M\subset X$ be a non-empty, weakly sequentially closed subset.
If $I:X\to \R_\infty$ is coercive on $M$ and weakly sequentially lower semicontinous, then there exists a minimizer $u_*\in M$ solving $I(u_*) = \inf_{\wt u \in M}I(\wt  u)$. 


\aaa{Poincar\'e inequality revisited.}
In the lecture, we have proven the Poincar\'e inequality on a bounded domain 
$\Omega$ in the form
\[
\forall\, u\in\rmW^{1,p}_0(\Omega):\quad \int_\Omega |u(x)|^p \dd x \leq C_\Omega^p \int_\Omega |\nabla u(x)|^p\dd x,
\]
where $C_\Omega=\mathrm{diam}(\Omega) = \sup\{|x{-}x'|\,|\,x,x'\in\Omega\}$.

\begin{itemize}
\item[(a)] Consider the functionals $I_p(u) = \int_\Omega |\nabla u|^p\dd x$ and $J_p(u) = \int_\Omega |u(x)|^p\dd x$ on $\rmW^{1,p}_0(\Omega)$. Show that there exists $u_*\in \rmW^{1,p}_0(\Omega)$ that minimizes $I_p$ over $\{u\in \rmW^{1,p}_0(\Omega)\,|\, J_p(u) = 1\}$. What is the connection to the Poincar\'e inequality above?

\item[(b)] For $p=2$ and $\Omega=\left]0,\ell\right[\subset \R^1$, show that the optimal constant $C_\text{opt}>0$ in the Poincar\'e inequality is $C_\text{opt} < C_\Omega =\ell$ by explicitly solving the Euler--Lagrange equations for $I_2$ and $J_2$.
\end{itemize}

\aaa{Gateaux and Fr\'echet differentials.}  Consider the Hilbert space $X=\rmL^2(\Omega;\R^m)$ and the 
functional $I(u)=\int_\Omega g(u(x))\dd x $, where $g\in \rmC^1(\R^m)$
satisfies 
\[
\exists\, C>0 \ \forall\, a,b\in \R^m:\quad |g(a{+}b)- g(a)| \leq
C(1{+}|a|) | b|.
\]
\begin{itemize}
\item [(a)] 
Establish the Gateaux differentiability with $\rmD^\rmG I(u)[v] =
\int_\Omega \pl_u g(u(x))\cdot v(x)\dd x$, i.e.\ for all $u,v\in X$ we have 
$\delta I(u;v):= \lim_{t\searrow 0} \frac1t \big( I(u{+}tv) - I(u)\big)
=  \rmD^\rmG I(u)[v]$.
\item[(b)] 
Show that $\rmD^\rmG I(u)$ is the Fr\'echet derivative $\rmD^\rmF
I(u)$ if additionally 
there exist $\theta\in {]0,1]}$ and $C>0$
such that $ |\pl_u g(a)-\pl_u g(b)| \leq C_2
\big(1{+}|a|{+}|b|\big) ^{1-\theta} |a{-}b|^\theta$ for all $a,b\in
\R^m$.
\item[(c)] 
Now consider the case $X=\rmL^1(\Omega)$ with $\Omega={]0,\ell[}
\subset \R^1$ and the functional $I(u)=\int_\Omega g(u(x)) \dd x $
with $g(u)=u^3/(1{+}u^2)$. Show that $I$ is Gateaux differentiable at
$u=0$ but not Fr\'echet differentiable. 
%
\end{itemize}

\aaa{Variational inequalities}. Let $X$ be a reflexive Banach space and $K\subset X$
be a closed and convex subset. Let $I:X\to \R$ be convex and Fr\'echet differentiable on $X$.

\begin{itemize}
\item[(a)]Show that the minimizer $u_*\in K$ satisfies
\[
I(u_*) = \inf_{\wt u\in K} I(\wt u)~\Leftrightarrow~
\rmD^\rmF I(u_*)[v{-}u_*]\geq 0~\forall\, v\in K~\Leftrightarrow~
-\rmD^\rmF I(u_*)\in\mathrm{N}_K(u_*)\subset X',
\]
where $\mathrm{N}_K(u_*) :=\{\ell\in X'\,|\,\ell(v{-}u_*)\geq 0 ~\forall v\in K\}$ is the outer normal cone of $K$ in $u_*\in X$.
\item[(b)] Let $\chi_K:X\to \{0,+\infty\}$ denote the convex indicator function of the set $K$, i.e.,
$\chi_K(u) = 0$ if $u\in K$ and $\chi_K(u) =+\infty$ otherwise. Show that $\chi_K$ is a convex and lower semicontinuous functional on $X$ and that the subdifferential of $\chi_K$
is given by the outer normal cone.
\item[(c)] Consider the functional $\wt I:X\to \R_\infty$ given via $\wt I(u) = I(u)+\chi_K(u)$. Show that 
$u_*$ minimizes $\wt I$ if and only if it minimizes $I$ over $K$.
\end{itemize}
\end{document}