\documentclass[12pt,a4paper]{article}


\input{../header.tex}

\begin{document}

\exerciseSet{3}{November 7, 2022}

\setcounter{AUFGABE}{6}

\aaa{Local convexity estimate.}
Let $X$ be a Banach space and let
$I:X\to\R$ be convex, i.e.
\[
I\big((1{-}\lambda)u_0 + \lambda u_1\big)\leq (1{-}\lambda)I(u_0)+ \lambda I(u_1)
\]
for all $u_0,u_1\in X$ and $\lambda\in(0,1)$.
Conclude: Every critical  point $u_\ast$ is a minimizer of $I$.
\textit{Hint:} First show 
$I(v)\geq I(u)+ \mathrm{D}I(u)[v{-}u]$
if $\mathrm{D}I(u)[v{-}u]$ exists.


\aaa{Noether's theorem for rotationally invariant systems.} The
density $f\in \rmC^2([\alpha,\beta]\times\R^m\times\R^m;\R)$ with
$m\geq 2$ defines
the functional  $I(u)=\int_{\alpha}^{\beta} f(t,u(t),\dot{u}(t))\dd t$.
For the rotation matrix  $R_{\varphi}\in\R^{m\times{}m}$ with 
\[
R_{\varphi}(y_1,y_2,y_3,...,y_m)^\top= ( \cos\varphi \,y_1 -\sin\varphi\, y_2,
\sin\varphi\, y_1 + \cos\varphi\, y_2,y_3,..., y_m)^\top, \  \varphi\in
\R,\ y\in \R^m,
\]
the density $f$ satisfies the rotational symmetry 
$f(t,R_\varphi{}u,R_\varphi{}A)=f(t,u,A)$ for all $t,u,A,\varphi$.

\begin{itemize}
\item[(a)]  Show that along solutions  $u:[\alpha,\beta]\to\R^m$ of the
\textsc{Euler--Lagrange} equation we have conservation of the moment
of momentum (Drehimpulserhaltung):
\[
\frac{\rmd }{\rmd t} \left[ u_1(t)\partial_{A_2}f(t,u(t),\dot{u}(t)) - 
u_2(t)\partial_{A_1}f(t,u(t),\dot{u}(t))\right]= 0.
\]
\emph{Hint: Calculate first $\frac{\rmd}{\rmd \varphi} 
f(t,R_\varphi{}u,R_\varphi{}A)\big|_{\varphi=0}$.}


\item[(b)] Now consider $R_\varphi=\ee^{\varphi{}B}\in\R^{m\times{}m}$ for a
  general $B\in\R^{m\times{}m}$ with $B=-B^\top$ and assume the
  symmetry 
$f(t,R_\varphi{}u,R_\varphi{}A)=f(t,u,A)$. Which quantity  $J(u,\dot{u})$
is now conserved?
\end{itemize}

\aaa{Second variation.}
Consider the functional $I:C^1(\overline\Omega;\R^m) \to \R$ with
$I(u) = \int_\Omega f(x,u(x),\nabla u(x))\dd x$, where $f\in
C^2(\ol\Omega\ti\R^m\ti \R^{m\ti d})$. 
For $\gamma_1, \gamma_2 > 0$ assume the estimates
\begin{align}
  \label{a14.bed1}
   \int_\Omega \rmD_A^2f(x,u_0(x),\nabla u_0(x)) [\nabla w]\dd
   x & \geq \gamma_1\int_\Omega |\nabla w|^2\dd x ,\\ 
  \label{a14.bed2}
  \rmD^2I(u_0)[w] & \geq \gamma_2 \int_\Omega |w|^2 \dd x.
\end{align}
\begin{itemize}
\item[(a)] Use $(\ref{a14.bed1})$ and find estimates for  $\pl_A\pl_uf$
and $\pl^2_u f$ to obtain a constant $C^*$ such that 
\[
\rmD^2 I(u_0)[w] \geq \gamma_1/2 \int_\Omega |\nabla w|^2\dd x 
- C^* |w|^2 \dd x \quad\text{ for all }w\in C^1(\overline\Omega;\R^m).
\]
\item[(b)] Combine \eqref{a14.bed2} and \eqref{a14.bed1} to find  $\gamma_3 >
0$, such that 
\[
\rmD^2I(u_0)[w] \geq \gamma_3\int_\Omega |\nabla w|^2
{+} |w|^2 \dd x \ \ \text{   for all } w\in C^1(\overline{\Omega};\R^m).
\]
\end{itemize}

\aaa{Weak and strong local minimizers.} 
Consider $M= \rmC^1([a,b];\R)$, functions 
$g,h \in \rmC^2(\R;\R)$,  and the functional $I:M\to\R$ defined via
\[
 I(u) = \int_a^b g(u'(x)) + h(u(x))\dd x. 
\]
\begin{itemize}
\item[(a)] Derive the associated \textsc{Euler--Lagrange} equation. Which
conditions guarantee that solutions of the form $u(x)=u_* =
\mathrm{const}$ exist?
\item[(b)] Assume that $u(x) = u_* = \mathrm{const}$ is a critical point
  of $I$. Show that the conditions 
$h''(u_*) > 0$ and $g''(0) > 0$ are sufficient to imply that $I$ has a
strict weak local minimizer in $u_*$.
\item[(c)]
Assume now that $g(A) \ge 0=g(0)$ for all $A \in
  \R^{1\times{}1}$ and that $u^0$ is a local minimizer of $h$.
Show that the constant function $\ol u:x\mapsto u^0$ is a strong local
minimizer. What additional conditions imply that $\ol u$ is a global
minimizer? 
\end{itemize}

\end{document}
